---
title: "LBB_P4DS"
author: "Amalia Purieka"
date: "4/12/2021"
output: 
 html_document:
   df_print: paged
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Background

AMPM is a Marketplace that loves to give out amazing deals. They have various discounts on every category, and They want their customer to get a fantastic bargain and expect an increasing Quantity of sales. AMPM works to satisfy its users. They want to make fast-moving products so that AMPM users will have more quantity sold and still profitable. This will be a win-win situation for both.

## Discount strategies

Plan before you offer discounts
Understand how discounting affects profit margins and sales targets
Consider the discount
Benefit discount to profit

## Import Library

```{r}
library(dplyr)
```


## Load Data

```{r}
retail <- read.csv("data_input/retail.csv")
```

read data retail and put to retail table

## Data Inspection

```{r}
str(retail)
```
check retail table structure

From our inspection we can conclude :

Retail data contain 9994 of rows and 15 of coloumns
Each of column name :
Row.ID
Order.ID
Order.Date
Ship.Date
Customer.ID
Segment
Product.ID
Category
Sub.Category
Product.Name
Sales
Quantity
Discount
Profit

## Data Cleansing AND Coertions

```{r}
retail$Row.ID <- as.character(retail$Row.ID)
retail$Order.ID<- as.character(retail$Order.ID)
retail$Order.Date<- as.Date(retail$Order.Date, "%m/%d/%y")
retail$Ship.Date <- as.Date(retail$Ship.Date, "%m/%d/%y")
retail$Customer.ID<-as.character(retail$Customer.ID)
retail$Product.ID<- as.character(retail$Product.ID)
retail$Product.Name<-as.character(retail$Product.Name)
```

change some data type in retail table

```{r}
str(retail)
```

check new structure in retail table

Check Missing Value

```{r}
colSums(is.na(retail))
```

no missing value in retail table

```{r}
retail <- retail %>% 
  select(-Row.ID, -Order.ID)
```

we erase two column, Row.ID and Order.ID because we dont use it.

## Data Explanatory

```{r}
retail <- retail %>% 
  mutate(PL = ifelse(Profit>= 0, "PROFIT","LOSS"))
table(retail$PL)
```

total sku that loss in profit 1871
total sku that get profit 8123

```{r}
retail.profit <- retail %>% 
  filter(PL == "PROFIT") %>%
  summarize(sum_profit = sum(Profit))

retail.loss <-  retail %>% 
  filter(PL == "LOSS") %>%
  summarize(sum_loss = sum(Profit))
  
x = retail.profit$sum_profit + retail.loss$sum_loss
x
```

so from this data we get Profit 286.397 if we combine sku with loss and profit

## Data Manipulation

```{r}
retail <- retail %>% 
  mutate(pos_profit = ifelse(Profit< 0, "negative","positive"))
```

to mutate new column fill it with negative profit or positive profit refer to profit or loss

```{r}
retail_profit <- retail %>% 
  select(Sales, Profit,pos_profit, Segment,Category, Sub.Category,Discount) %>% 
  filter(Discount > 0) %>% 
  filter(pos_profit == "positive") %>% 
  mutate(COGS = Sales - Profit, a = 1- Discount, mftdisc = Profit / Sales,sales_bfr = Sales/a) %>% 
  mutate(sales_bfr = formatC(sales_bfr, digits = 4, format = "f"))

head(retail_profit)
```

this chunk find a profit sku after discount company gift and adding some column adding some column to gain some information:
cogs = cost of good sold
mftdisc = margin after discount
sales_bfr = sales before discount

```{r}
retail_loss <- retail %>% 
  select(Sales, Profit,pos_profit, Segment,Category, Sub.Category,Discount) %>% 
  filter(Discount > 0) %>% 
  filter(pos_profit == "negative") %>% 
  mutate(hpp = Sales - Profit, a = 1- Discount, mftdisc = Profit / Sales,sales_bfr = Sales/a) %>% 
  mutate(sales_bfr = formatC(sales_bfr, digits = 4, format = "f"))

head(retail_loss)
```

this chunk find a loss in profit sku after discount company gift and adding some column
adding some column to gain some information:

cogs = cost of good sold
mftdisc = margin after discount
sales_bfr = sales before discount

```{r}
max_profit <- max(retail_profit$Profit)
retail_profit1 <- retail_profit %>% 
  select(Sales, Profit,pos_profit, Segment,Category,mftdisc, Sub.Category,Discount) %>% 
  filter(Profit == max_profit)

retail_profit1
```
Technolgy/copiers has a maximum profit with discount 0.2

```{r}
max_loss <- min(retail_loss$Profit)
retail_loss1 <- retail_loss %>% 
  select(Sales, Profit,pos_profit, Segment,Category,mftdisc, Sub.Category,Discount) %>% 
  filter(Profit == max_loss)

retail_loss1
```

Technology/Machine has minimum profit with discount 0.7

## Business Recommendation

some information we have after AMPM:

- so from this data, we get Profit 286.397 despite the fact that some SKU got a loss
- find Cost of good sold
- find margin after Discount
- find loss or profit
- find category with profit or loss SKU

The Discount must be less than the initial margin if you want to keep making a profit, by adding Cost of good sold information obtained from Sales - Profit, find out the initial margin by adding this margin in the data frame that can be used as a benchmark in this company to place a discount in the upcoming discount program. From this data, it can be seen that there is a negative profit because the Discount is greater than the initial margin.